Verifying Demonstrations

### 2018-11-16 paper/privacy-properties.tex
Removes @dbosk's arguments and slightly adapts @sbuc's statements
I remove @dbosk's arguments against @sbuc's statements about receipt
freeness and verifiability.

I also slightly adapts them:

  - Footnote on desirable, stating it's probably impossible without
  violating verifiability.
  - Still don't make clear which verifiability: @dbosk argues
  eligibility, @sbuc individual verifiability.

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
%Seb: ok but if Alice can refuse to upload her participation proof then coercion resistance can still be achieved
Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there), which conflicts with verifiability.
\daniel{%
  No, that implication is not true, counter example:
  There is receipt freeness for how an elector voted, but not that they voted.
  As Simon pointed out, they tick me off, so it's visible that I've voted.
  But no one will ever know for which party I voted.%
}

\daniel{%
  This doesn't conflict with verifiability either.
  I keep track of the ballot box, as long as that and all ballots inside are 
  treated properly, I know my ballot is safe and counted.%
}

\daniel{%
  In our case:
  I have a key issued on a smartcard and it is tied to my identity.
  If the hardware corrupts itself after issuing the \ac{NIZK} proof, then there 
  is no way to check whether I created \(\pid = \ACprf[_k][\cid]\) or \(\pid' = 
    \ACprf[_k][\cid']\).
  I could have downloaded both from the ledger.
  But I know which is mine, I can submit it, and as long as the block where it 
  was included is intact I know my proof-share is included as well --- even if 
  I forget what it looked like.%
}

>>>>

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness, while appealing at first glance, is not desirable\footnote{%
  Or not possible without violating some of the verifiability 
  requirements.
} in our context since this will conflict with verifiability: in contrast to 
voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the 
protest) implies receipt freeness for \emph{that} the voter voted (\ie the 
protester was there), which conflicts with verifiability.
